Racauo Amicus Brief Models

### 2022-05-18 modeling/amicus_type/other-authors/aclauf.Rmd
move author types we removed

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(aclauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

@@

```{r}
data_scale <- data %>%
  mutate(across(c(where(is.numeric), -justicevot, -id),
                ~(scale(., center=T, scale=T) %>% as.vector)))

data_scale <- janitor::remove_empty(data_scale, which = "cols")
```

@@

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
data <- box_read(amicus_only) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(aclauf_abortion_different:aclauf_womens_rights), ~replace_na(.x, 0)))
```

@@

```{r}
data <- data %>%
  select(case:cirsplit, aclauf_abortion_different:aclauf_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('aclauf')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('aclauf')) %>% colnames()
setdiff(total_cols, remaining_cols)
```

@@

```{r, eval=F}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                aclauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-18 modeling/amicus_type/other-authors/chcauf.Rmd
move author types we removed

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(chcauf_abortion_different:chcauf_womens_rights), ~replace_na(.x, 0)))
```

Add Case ID-- this will be the second level var

```{r}
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
#data %>% head(1) %>% select(case:justicefem)
```

@@

```{r}
data <- data %>%
  select(case:cirsplit, pfemam, chcauf_abortion_different:chcauf_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('chcauf')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('chcauf')) %>% colnames()
setdiff(total_cols, remaining_cols)
```

@@

* 0:
* 0.01:
* 0.05: standing
* 0.10: 
* 0.20:

# Abortion different

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_abortion_different + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod1,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod1)
```

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_abortion_regret + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_bad_law + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Comp Motherhood

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_compulsory_motherhood + pfemam,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Compulsory Motherhood II

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_compulsory_motherhood_ii + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_evidence + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_final_authority + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_morality_religion + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_overturn_roe + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_privacy + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_standing + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_uncertainty + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_undue_burden + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_untruthful + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_womens_future_life + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_womens_health + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                chcauf_womens_rights + pfemam,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
data <- box_read(final_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #sgfem3 = as.factor(sgfem3), 
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(chcauf_abortion_different:chcauf_womens_rights, 
                  fem_abortion_different:fem_womens_rights), ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

# add case ID (second level var)
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")
```

@@

```{r}
data <- data %>%
  select(case:cirsplit, pfemam, chcauf_abortion_different:chcauf_womens_rights, fem_abortion_different:fem_womens_rights) %>% 
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                ~(scale(., center=T, scale=T))))
                #~(scale(., center=T, scale=T) %>% as.vector)))

total_cols <- data %>% select(contains('chcauf')) %>% colnames()
data <- janitor::remove_empty(data, which = "cols")
remaining_cols <- data %>% select(contains('chcauf')) %>% colnames()
#setdiff(total_cols, remaining_cols)
```

@@

* 0:
* 0.01: standing (+)
* 0.05: 
* 0.10: 
* 0.20: overturn roe (+)

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_abortion_regret +
                chcauf_abortion_regret,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_bad_law + 
                chcauf_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval = F}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + chcauf_compulsory_motherhood + 
                chcauf_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval = F}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_compulsory_motherhood_ii + 
                chcauf_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod9 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_evidence + 
                chcauf_evidence,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

# Fetus

```{r}
mod11 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_fetus + 
                chcauf_fetus,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

tidy(mod11,conf.int=F,exponentiate=T,effects="fixed") %>% 
  mutate(across(where(is.numeric), ~round(.x, 4))) %>% 
  mutate(probability_yes = round(estimate/(1+estimate),4)) %>% 
  mutate(confidence = case_when(
    p.value >= 0 & p.value <= 0.001 ~ "***", 
    p.value > 0.001 & p.value <= 0.01 ~ "**",
    p.value > 0.01 & p.value <= 0.05 ~ "*",
    p.value > 0.05 & p.value <= 0.1 ~ ".",
    T ~ ""
  )) %>% 
  rename(odds_ratio = estimate) %>% 
  select(term, odds_ratio, p_value = p.value, confidence) %>% 
  kable()

summary(mod11)
```

@@

```{r}
mod12 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_final_authority +
                chcauf_final_authority,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod14 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_morality_religion + 
                chcauf_morality_religion,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod15 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_overturn_roe +
                chcauf_overturn_roe,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod18 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_privacy + 
                chcauf_privacy,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod20 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_standing +
                chcauf_standing,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_uncertainty +
                chcauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod23 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_undue_burden + 
                chcauf_undue_burden,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_untruthful + 
                chcauf_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_womens_future_life +
                chcauf_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod26 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_womens_health + 
                chcauf_womens_health,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + sgfem3 + lcdisdirfem + pfemam + fem_womens_rights + 
                chcauf_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-18 modeling/amicus_type/other-authors/govauf.Rmd
move author types we removed

```{r}
data <- box_read(full_cases) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(govauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

@@

* 0:
* 0.01:
* 0.05:
* 0.10:

@@

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r}
data <- box_read(amicus_only) %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2)) %>% 
  mutate(across(c(govauf_abortion_different:sgauo_womens_rights), ~replace_na(.x, 0)))
```

@@

* 0:
* 0.01:
* 0.05:
* 0.10: informed consent

@@

```{r, eval=F}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                govauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-18 modeling/amicus_type/other-authors/mpeauf.Rmd
move author types we removed

* 0:
* 0.01:
* 0.05:
* 0.10: bad law, physician, physician negative

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

* 0:
* 0.01:
* 0.05:
* 0.10: abortion different, bad law, physician negative

@@

```{r, eval=F}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod22 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                mpeauf_uncertainty,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

### 2022-05-18 modeling/amicus_type/other-authors/racauo.Rmd
move author types we removed

```{r}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

>>>>

```{r, eval=F}
mod1 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_abortion_different,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod3 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_anti_women,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod4 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_bad_law,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod5 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_bodily_integrity,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod6a <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_compulsory_motherhood,
              family = binomial, data = data,  
              nAGQ = 1, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod6b <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_compulsory_motherhood_ii,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod10 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_favor_childbirth,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod13 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_informed_consent,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod19 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_protesters,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod24 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_untruthful,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod25 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_womens_future_life,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))

@@

```{r, eval=F}
mod27 <- glmer(justicevot ~
                (1|id) + justicemq + justicefem + nonftyp2 + lcdisdirfem +
                racauo_womens_rights,
              family = binomial, data = data,  
              nAGQ = 0, control=glmerControl(
                check.conv.grad="ignore",check.conv.singular="ignore",check.conv.hess="ignore"))
